### 2016-07-06 version0.0/appendixa.tex
adding prelude to into. section

>>>>

\section{2D SOMs of subsets}
\label{sec: app_2d_soms_SOMN}

        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        For subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
        \import{../image_paper3/text_files/tables/}{subset2.tex}
        \import{../image_paper3/text_files/image_texts/}{subset2.tex}

        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
        \import{../image_paper3/text_files/tables/}{subset3.tex}
        \import{../image_paper3/text_files/image_texts/}{subset3.tex}

        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
        These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
        Since regions 1 and 2 have similar metallicity and total PAHs, and their total stellar mass are comparable, removing these values from input data made the position of the regions 1 and 2 moved further from each other. 
        \import{../image_paper3/text_files/tables/}{subset4.tex}
        \import{../image_paper3/text_files/image_texts/}{subset4.tex}

        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../image_paper3/text_files/tables/}{subset7.tex}
        \import{../image_paper3/text_files/image_texts/}{subset7.tex}

### 2016-07-06 version0.0/asli.tex
adding prelude to into. section

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
%\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=True,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
%\newcommand{\superj}{Dr. A. Manning} %joint supervisor, if there is one, leave blank if not (lbin)... only one of the three.
\newcommand{\superc}{} %co-supervisor, if there is one, leave blank if not (lbin)
\newcommand{\supera}{} %alternate supervisor, if there is one, leave blank if not (lbin)
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. S. Basu}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. S. Gallagher}
\newcommand{\examth}{Dr. M. Daley}
\newcommand{\examf}{}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{Properties of nearby galaxies from modern statistical methods:Bayesian analysis and Data Mining}
\newcommand{\spinetitle}{Properties of nearby galaxies}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} {
I would like to thank all my Friends in Western.
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and supports. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
\newcommand \sva {SvA}%: Soviet Astronomy

\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}

%% This generates the title page from the information given above.
\maketitle
\addcontentsline{toc}{chapter}{Certificate of Examination}
\makecert
\newpage
\addcontentsline{toc}{chapter}{Co-Authorship Statement}
\coauthor{\makecoauthor}  %comment this out if none
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\acknowlege{\makeacknowlege}	%as above
\newpage
\addcontentsline{toc}{chapter}{Dedication}
\dedications{\makededications}
\newpage
\addcontentsline{toc}{chapter}{Abstract}
\Large\begin{center}\textbf{Abstract}\end{center}\normalsize
%%  ***  Put your Abstract here.   ***
%% (150 words for M.Sc. and 350 words for Ph.D.)

I study properties of galaxies.

@@

\include{intro}
\include{paper1}
\include{paper2}

%% This adds a line for the Bibliography in the Table of Contents.
\addcontentsline{toc}{chapter}{Bibliography}
%% ***   Set the bibliography style.   ***
\bibliographystyle{apj.bst} % (change according to your preference)
%%% ***   Set the bibliography file.   ***
\bibliography{westernthesis}

>>>>

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} {
I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad,
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {S~{\textsc II}} 
\newcommand \oiii {O~{\textsc III}} 
\newcommand \hi {H~{\textsc I}\ }
\newcommand \hii {H~{\textsc II}\ }
\newcommand \oii {O~{\textsc II}}

\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}
\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

%% This generates the title page from the information given above.
\maketitle
\addcontentsline{toc}{chapter}{Certificate of Examination}
\makecert
\newpage
\addcontentsline{toc}{chapter}{Co-Authorship Statement}
\coauthor{\makecoauthor}  %comment this out if none
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\acknowlege{\makeacknowlege}	%as above
\newpage
\addcontentsline{toc}{chapter}{Dedication}
\dedications{\makededications}
\newpage
\addcontentsline{toc}{chapter}{Abstract}
\Large\begin{center}\textbf{Abstract}\end{center}\normalsize
%%  ***  Put your Abstract here.   ***
%% (150 words for M.Sc. and 350 words for Ph.D.)
Understanding the process of star formation is one of the key steps in understanding the formation and evolution of galaxies.
In this thesis, I address the empirical star formation laws, and study the properties of galaxies that can affect the star formation rate.

The Andromeda galaxy (M31) is the nearest large spiral galaxy, and Therefore, high resolution images of this galaxy are available.
These images provide data from various regions with different physical properties.
Star formation rate and gas mass surface densities of M31have been measured using three different methods, and have been used to compare different star formation laws over the whole galaxy and in spatially-resolved regions.
Using hierarchical Bayesian regression analysis, I conclude that there is a correlation between surface density of star formation and the stellar mass surface density.
A weak correlation between star formation rate, stellar mass and metallicity is also found.

To study the effect of other properties a galaxy on the star formation rate, I utilize an unsupervised data mining method (specifically the self-organizing map) on measurements of both nearby and high-redshift galaxies.
Both observed data and derived quantities (e.g. star formation rate, stellar mass) of star-forming regions in M31 and the nearby spiral galaxy M101 are used as inputs to the self-organizing map.
Clustering the M31 regions in the feature space reveals some (anti)-correlations between the properties the galaxy, which are not apparent when considering data from all regions in the galaxy. 
The self-organizing map can be used to predict star formation rates for spatially-resolved regions in galaxies using other properties of those regions.

I also apply the self-organizing map method to spectral energy distributions of high-redshift galaxies.
Template spectra made from galaxies with known morphological type are used to train self-organizing maps.
The trained maps are used to classify a sample of galaxy spectral energy distributions derived from fitting models to photometry data of 142 high-redshift galaxies.
The grouped properties of the classified galaxies are found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.

@@

\include{intro0.0}
%\include{paper1}
%\include{paper3}
%\include{paper2}

%% This adds a line for the Bibliography in the Table of Contents.
%\addcontentsline{toc}{chapter}{Bibliography}
%% ***   Set the bibliography style.   ***
%\bibliographystyle{apj.bst} % (change according to your preference)
%%% ***   Set the bibliography file.   ***
%\bibliography{westernthesis}
